Measuring Perceptions and Preferences for Meritocracy

### 2021-09-23 paper.Rmd

_b. Beliefs?_

@@

_c. Non-meritocratic aspects_

@@

_d. Accounting for measurement error_

@@

  knitr::kable(tab.inv, col.names = col.nam, align = "l",
        booktabs=TRUE,format = table_format,escape = FALSE,
        caption = "Multiple Group meassurement invariance for Perceptions and Preferences for Meritocracy") %>%
    kableExtra::kable_styling(full_width = FALSE,latex_options = "HOLD_position",bootstrap_options=c("striped", "bordered")) %>%
    kableExtra::footnote(general = footnote, footnote_as_chunk = T)
```

>>>>

b. _Beliefs?_

@@

c. _Non-meritocratic aspects_

@@

d. _Accounting for measurement error_

@@

  knitr::kable(tab.inv, col.names = col.nam, align = "l",
        booktabs=TRUE,format = table_format,escape = FALSE,
        caption = "Multiple Group meassurement invariance for Perceptions and Preferences for Meritocracy") %>%
    kableExtra::kable_styling(full_width = FALSE,
                              latex_options = "HOLD_position",
                              bootstrap_options=c("striped", "bordered"),
                              font_size = 10) %>%
    kableExtra::footnote(general = footnote, footnote_as_chunk = T)
```
